|

### 2025-01-31 doc/paper.qmd
task 1 text

## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
Following @ball_how_2008, I focus the analysis on earnings announcements and stock returns from 1972 to 2006, ensuring that the data accurately reflects the original study’s methodology and findings. The replication aims to mirror the research design as closely as possible with the available data, maintaining consistency in sample selection, event window definitions, and return calculations.

Based on the original paper, I do not gather analyst expectations or estimate earnings deviations for my replication. Instead, I only require stock return data and earnings announcement dates, which simplifies the data collection process.

In addition, I impose the following assumptions to ensure clarity and consistency where @ball_how_2008 do not provide explicit guidance:

1. Following @ball_how_2008, I define earnings announcement windows as the three-day period surrounding the earnings release (-1 to +1), where Day -1 is the last trading day before the announcement, Day 0 is the announcement day, and Day +1 is the first trading day after the announcement. According to @center_for_research_in_security_prices_crsp_crsp_2024 guide, data are never provided on weekends or trading holidays, meaning there is no need for manual filtering of such days. However, if an earnings announcement falls on a non-trading day, adjustments are necessary to maintain the three-day window. Hence, earnings announcement dates are first extracted from Compustat and then matched with CRSP trading data to obtain stock returns for the event window (-1, 0, +1). If Day 0 falls on a weekend or holiday, it is shifted to the next available trading day. Similarly, if Day -1 or Day +1 is unavailable due to a non-trading day, the nearest prior or next trading day, respectively, is used to preserve the event window.

2. As in the original paper, firm-years are selected based on available stock return data in CRSP. While @ball_how_2008 restrict the sample to firms with at least 240 trading days per year, I follow the course guidance and do not apply this restriction, allowing for a slightly larger sample size. This adjustment should be considered when interpreting differences from the original study.

3. Compustat includes both active and inactive firms, and the original study does not specify filtering based on firm activity. Thus, all firms meeting the sample selection criteria (i.e., four quarterly earnings announcements per year and available stock return data) are retained, regardless of their active status today.

4. For historical analysis on securities, permanent identifiers, such as `PERMNO`, `PERMCO`, and `GVKEY` are used that never change for the duration of the company’s life span regardless of the name changes and are never being reused [@gow_empirical_2025]. In this replication, variable `PERMNO` is used instead of `PERMCO` because it uniquely identifies individual securities rather than companies, ensuring that stock returns are accurately tracked at the security level. Since firms may have multiple share classes with distinct price movements, using `PERMNO` prevents aggregation issues that could arise with `PERMCO`, which groups all share classes under one identifier.

5. The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database, but with different update frequencies: Compustat (daily), CRSP (annually), and CCM (annually). Timing mismatches may arise, especially for firms with restated financials, leading to possible variations in event window alignment when calculating earnings-announcement returns. Unlike the original study, this replication uses the latest WRDS version available as of January 2025, meaning database updates may cause differences in firm coverage or reported values.

@@

## Results {#sec-results1}
Comparing the replication results of Figure 1 (see @fig-market-shares) with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies.

@@

@fig-market-shares illustrates the... Countries are sorted in a specific order reflecting the replication of Figure 3 from the European Commission’s 2024 report.

To verify the results of analysis step and observe trends before plotting, I have additionally saved the CSV output in `aggregated_market_shares.csv`. The analysis of market shares for statutory audits across European countries reveals distinct patterns of market concentration and auditor dominance. Big 4 firms exhibit a significant presence, often commanding a dominant share in many countries. For example, countries such as the Czech Republic, Estonia, and Finland demonstrate Big 4 market shares exceeding 95%, reflecting the significant influence of these firms in specific markets. However, the extent of this dominance varies, with lower Big 4 shares observed in countries like Bulgaria (17.5%) and Greece (43.6%), indicating a more diversified audit market in these regions. The analysis reveals that the Big 4 hold a market share exceeding 80% in 11 EU countries. This aligns with rthe finding of @EC_Report_2024, which similarly highlights that the Big 4 dominate over 80% of the market share in 11 Member States.

The inclusion of additional audit networks through the 10KAP grouping increases the market share substantially across all countries, as expected. This is particularly evident in countries like Ireland, Malta, and the Netherlands, where the 10KAP share reaches 100%, reflecting the full inclusion of statutory audits under this grouping. In contrast, countries like Bulgaria and Poland, with 10KAP shares of 41.8% and 63.6%, respectively, suggest the presence of a substantial number of statutory audits conducted by unaffiliated or smaller firms.

In the analysis of CR4 market shares, I verified whether the four largest audit firms (CR4) in each country overlapped entirely with the Big 4 audit firms. This overlap occurred in 15 out of 28 countries, where CR4 and Big 4 market shares were identical. In the remaining 13 countries, at least one non-Big 4 firm contributed significantly to the statutory audits, resulting in distinct CR4 market shares. These findings align with @EC_Report_2024, which notes that in 13 Member States, the Big Four are not the four largest audit firms in terms of the total number of PIE statutory audit opinions. This highlights the gradual diversification in the audit market in some countries, where non-Big 4 firms are playing a more prominent role, while the Big 4 continue to dominate in others.

At the EU level, the aggregated market shares further underscore the dominance of these major players. The Big 4 account for 70% of statutory audits, compared to @EC_Report_2024, which notes an average EU market share of 59% for the Big 4 in 2021, down from 70% in 2018. The broader 10KAP grouping in my output reaches nearly 90%, exceeding the 81% reported by @EC_Report_2024. The CR4 market share at the EU level also stands at 70%, aligning with the Big 4, and is consistent with the average CR4 market share reported by @EC_Report_2024. These results highlight the varying degrees of market concentration across Europe, with certain countries demonstrating a highly centralized audit market dominated by the Big 4, while others display a more distributed market landscape, incorporating both major and smaller audit firms. The slight discrepancies in the figures suggest potential differences in methodologies, data coverage, or sample definitions.

Based on the results for Austria, the Big 4 market share is 86.7% in my analysis, aligning closely with the approximate 85% represented in bar chart of @EC_Report_2024. Similarly, the 10KAP market share of 92.55% in my analysis corresponds well with the slightly higher bar in the report, and the CR4 market share of 86.7% aligns perfectly with the Big 4 share, confirming the dominance of these firms in Austria’s audit market. This consistency highlights the robustness of the replicated analysis for this country.

The results for Romania show notable discrepancies. The EC Report indicates market shares of 15% for the Big 4, 16% for CR4, and 24% for 10KAP, while my analysis reports significantly higher values: 63%, 70.61%, and 78.38%, respectively. These differences likely arise from assumptions made in @sec-research_design_assumptions like variations in PIE definitions and auditor classifications. The report by @EC_Report_2024 may use stricter criteria, reflecting Romania’s decentralized market where non-Big 4 firms dominate, unlike the broader inclusion in my dataset.

In summary, the replication effectively captures the original report's key findings, confirming the dominance of the Big 4 and the broader 10KAP group in the European audit market. The analysis highlights varying degrees of market concentration across countries, with some demonstrating a more decentralized audit landscape. While discrepancies in individual country results, such as Romania, underline the importance of methodological alignment, the strong similarity between the overall market shares reported in the original report and the replicated results underscores the robustness and reliability of the findings.
qqq we confirm? "The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market. By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system. The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons. By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking. Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."

@@

>>>>

## Research Design Choices and Assumptions {#sec-research_design_assumptions1}
Following @ball_how_2008, I focus on earnings announcements and stock returns from 1972 to 2006, ensuring alignment with the original study’s methodology. This replication mirrors the research design, maintaining consistency in sample selection, event window definitions, and return calculations.

Based on the original paper, I do not gather analyst expectations or estimate earnings deviations, requiring only stock return data and earnings announcement dates, simplifying data collection.

To ensure clarity where @ball_how_2008 lacks explicit guidance, I impose the following assumptions:

1.	Earnings announcement windows are defined as the three-day period surrounding the release (-1 to +1). According to @center_for_research_in_security_prices_crsp_crsp_2024 guide,since CRSP excludes weekends and holidays, if Day 0 falls on a non-trading day, it shifts to the next trading day. Similarly, Day -1 or +1 adjusts to the nearest available trading day.

2.	Firm-years are selected based on available CRSP stock return data. While @ball_how_2008 restricts the sample to firms with at least 240 trading days per year, I follow course guidance and do not impose this restriction, allowing for a slightly larger sample.

3.	Compustat includes active and inactive firms; since the original study does not filter based on firm activity, all firms meeting sample selection criteria (four quarterly earnings announcements per year, available stock returns) are retained.

4.	Permanent identifiers (`PERMNO`, `PERMCO`, `GVKEY`) ensure accurate historical tracking [@gow_empirical_2025]. `PERMNO` is used instead of `PERMCO` as it uniquely identifies individual securities rather than companies, preventing aggregation issues from multiple share classes.

5.	The replication relies on Compustat and CRSP, linked via the CRSP/Compustat Merged (CCM) database. As Compustat updates daily, while CRSP and CCM update annually, timing mismatches may arise. Unlike the original study, this replication uses the latest WRDS version as of January 2025, meaning database updates may introduce firm coverage or value differences.

@@

## Results {#sec-results1}
Since Tables and Figure replication not finished, this section presents only the original @fig-fig1_original.

@@

@@

qqq we confirm? "The results are consistent with the view that the primary economic role of reported earnings is not to provide timely new information to the share market. By inference, that role lies elsewhere, for example, in settling debt and compensation contracts and in disciplining prior information,including more timely managerial disclosures of information originating in the firm’s accounting system. The comparatively low “surprise” content of earnings announcements is to be expected, for a variety of reasons. By its nature, accounting earnings is low frequency (quarterly), not discretionary (announced every quarter, independent of whether there is substantial new information to report), and primarily backward-looking. Other information, and hence revision in share price, is comparatively high frequency, frequently discretionary (released only when there is substantial information to report), and both forward-looking and backward-looking."
